---
title: "Demo of simulations in group sequantial design"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    number_sections: true
    highlight: "textmate"
    css: "custom.css"
# bibliography: "example.bib"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{What the Vignette Does (Title Case)}
---
```{r, message=FALSE}
library(distsurv)
library(tidygsd)
library(dplyr)
```

# Initialize a design for simulations

We initialize a design in simulations by input its `n_sim` and `sample_size` first.
```{r}
x <- Design$new(n_sim = 10, 
                sample_size = 200)
x
```

```{r}
x$n_sim
x$sample_size
```
# Input strata parameters
```{r}
x |> input_stratum(name = c("Biomarker-positive", "Biomarker-negative"),
                   ratio = 4:5)
```

# Define enrollment 

When input the enrollment rates over time, we assume the enrollment rate is the same across all strata and arms.

```{r}
my_enroll <- distsurv::PiecewiseExponential$new(duration = c(4, 6), rate = c(8, 3))

my_enroll %>% summary()
```

```{r}
x <- x %>% input_enroll(dist = my_enroll)

x
```

```{r}
x$enroll %>% summary()
```

# Define the failure 

In this example, we assume the failure rate is different by arms and 2 strata (biomarker positive/negative).

```{r}
my_fail_ctl_pos <- distsurv::PiecewiseExponential$new(duration = c(3, 3), rate = c(0.05, 0.03))
my_fail_ctl_neg <- distsurv::PiecewiseExponential$new(duration = c(3, 3), rate = c(0.06, 0.05))
my_fail_exp_pos <- distsurv::PiecewiseExponential$new(duration = c(3, 3), rate = c(0.04, 0.01))
my_fail_exp_neg <- distsurv::PiecewiseExponential$new(duration = c(3, 3), rate = c(0.05, 0.03))
```

```{r, message=FALSE}
x <- x |>
  input_failure(arm = "Control",
                stratum = "Biomarker-positive",
                dist = my_fail_ctl_pos) |>
  input_failure(arm = "Control",
                stratum = "Biomarker-negative",
                dist = my_fail_ctl_neg) |>
  input_failure(arm = "Experimental",
                stratum = "Biomarker-positive",
                dist = my_fail_exp_pos) |>
  input_failure(arm = "Experimental",
                stratum = "Biomarker-negative",
                dist = my_fail_exp_neg) 

x
```

```{r}
x$failure
```

# Define the dropout rates over time

```{r}
my_dropout_ctl_pos <- distsurv::PiecewiseExponential$new(duration = 100, rate = 0.002)
my_dropout_ctl_neg <- distsurv::PiecewiseExponential$new(duration = 100, rate = 0.0025)
my_dropout_exp_pos <- distsurv::PiecewiseExponential$new(duration = 100, rate = 0.001)
my_dropout_exp_neg <- distsurv::PiecewiseExponential$new(duration = 100, rate = 0.0015)
```

```{r, message=FALSE}
x <- x |>
  input_dropout(arm = "Control",
                stratum = "Biomarker-positive",
                dist = my_dropout_ctl_pos) |>
  input_dropout(arm = "Control",
                stratum = "Biomarker-negative",
                dist = my_dropout_ctl_neg) |>
  input_dropout(arm = "Experimental",
                stratum = "Biomarker-positive",
                dist = my_dropout_exp_pos) |>
  input_dropout(arm = "Experimental",
                stratum = "Biomarker-negative",
                dist = my_dropout_exp_neg) 

x
```

```{r}
x$dropout
```


# Simulate stratified TTE outcome in randomized trials
```{r}
set.seed(123)
x %>% generate_tte(block = c(rep("Control", 2), rep("Experimental", 2)))
```

# References
```{r}
set.seed(123)
simtrial::simPWSurv(n = 200,
                    strata = tibble(Stratum = c("Positive", "Negative"), p = c(.3, .7)),
                    block = c(rep("Control", 2), rep("Experimental", 2)),
                    enrollRates = tibble(Stratum = "All", rate = c(8, 3), duration = c(4, 6)),
                    failRates = tibble(Stratum = c("Positive", "Positive", "Negative", "Negative", "Positive", "Positive", "Negative", "Negative"),
                                       period = rep(1:2, 4),
                                       Treatment = rep(c("Control", "Experimental"), each = 4),
                                       duration = rep(c(3, 3), 4),
                                       rate = c(.05, .03, .06, .05, .04, .01, .05, .03)),
                    dropoutRates = tibble(Stratum = c(rep("Positive", 2), rep("Negative", 2)),
                                          period = rep(1, 4),
                                          Treatment = rep(c("Control", "Experimental"), 2),
                                          duration = rep(100, 4),
                                          rate = c(0.002, 0.001, 0.0025, 0.0015)))
```

